Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-05-24 manuscript/manuscript.tex
Modifications in Conclusions

For this reason we have developed a density-based discretization algorithm that 
divides the tesseroid on the radius at which the \emph{maximum variation} of 
the density function takes place, only if a certain inequation that relates 
this \emph{maximum variation} with a predefined delta ratio $\delta$ holds.
The the number of subdivisions is indirectly controlled by this delta 
ratio $\delta$, and thus the accuracy of the computation.
This new algorithm is intended to minimise the error due to the inability of 
the GLQ to produce precise approximations in case of highly varying density: 
the information about the density function is summed up with the values that 
it assumes at the node of the quadrature.
Increasing the subdivisions of the tesseroid where the \emph{maximum 
variation} of the density takes place becomes an efficient way to reduce this 
kind of error.

@@

In the linear density case, the densty-based discretization algorithm is not 
applied due to how it's build, so only a default value of $D$ had to be 
determined.
By comparing the analytical solutions of the gravitational fields generated by 
a spherical shell with the ones produced by the numerical model for different 
values of $D$, we have obtained default values for the distance-size ratio of 
1, 2 and 8 for the potential, its gradient and the Marussi tensor components, 
respectively.
From these comparisons we can guarantee a precision of 0.1\% or greater on the 
computations of the gravitational fields generated by a tesseroid with a 
linear density.

@@

Finally, we have shown how this new method performs under a real data example: 
we have computed the gravitational fields generated by the Neuqu\'en 
sedimentary basin through a tesseroid model with an increasing exponential 
density in depth on a regular grid at 50km height.

>>>>

For this reason we have developed a density-based discretization algorithm that 
divides the tesseroid on the radius at which the \emph{maximum variation} of 
the density function takes place, only if a certain inequation that relates 
this \emph{maximum variation} with a predefined delta ratio $\delta$ holds.
The number of subdivisions is indirectly controlled by this delta 
ratio $\delta$, and thus the accuracy of the computation.
This new algorithm is intended to minimise the error due to the inability of 
the GLQ to produce precise approximations in case of highly varying density: 
the information about the density function is summed up with the values that 
it assumes at the node of the quadrature.
Increasing the subdivisions of the tesseroid where the \emph{maximum 
variation} of the density takes place becomes an efficient way to reduce this 
kind of error.

@@

In the linear density case, the densty-based discretization algorithm is not 
applied due to how it's build, so only a default value of $D$ had to be 
determined.
By comparing the analytical solutions of the gravitational fields generated by 
a spherical shell with the ones produced by the numerical model for different 
values of $D$, we have obtained default values for the distance-size ratio of 
1, 2 and 8 for the potential, its gradient and the Marussi tensor components, 
respectively.
From these comparisons we can guarantee a precision of 0.1\% or greater on the 
computations of the gravitational fields generated by any tesseroid with a 
linear density.

@@

In order to implement this new methodology we have developed a Python code 
that carries out both discretization algorithms and the gravitational field 
computation through the GLQ. It's freely available under the BSD 3-clause 
open-source license and can be downloaded from
\todo[inline]{add repo url}

Finally, we have shown how this new method performs under a real data example: 
we have computed the gravitational fields generated by the Neuqu\'en 
sedimentary basin through a tesseroid model with an increasing exponential 
density in depth on a regular grid at a computation height of 50km over the 
reference ellipsoid.
